Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-02-26 TEBenchmarkPaper/article.tex
ATE -> MTE

\begin{abstract}
  We propose a benchmark suite for evaluating the efficiency and effectiveness
  of automated tools for \emph{theory exploration} or
  \emph{conjecture formation} in higher-order, inductive theories; a domain
  especially suited for analysing software. By providing standard tools and
  metrics, we hope to encourage innovation and comparison between the disparate
  approaches currently being pursued, and spur improvements similar to those
  seen in the competitive field of automated theorem proving.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\emph{Mathematical theory exploration} (MTE), also known as
\emph{conjecture generation/formation}, is the open-ended problem of producing
conjectures about a given logical theory which are somehow ``interesting''.

This has applications wherever we find use for formal statements: in proof
assistants and their libraries, in mathematics education and research, and
(of special concern for the authors) in the specification, verification,
optimisation and testing of software.

@@

We attempt to solve this discrepancy, at least for the foreseeable future, by
defining a standard, unambiguous benchmarking approach with which to compare
ATE systems. Our contributions include:

\begin{itemize}
\item A general methodology for benchmarking ATE systems.
\item Resolving the issue of ``interestingness'' through the use of
  theorem-proving benchmarks as a ground-truth.
\item A specific instantiation of this methodology, using the Tons of Inductive
  Problems benchmark as a corpus.
\item Automated tooling to perform this benchmarking.
\item Application of our methodology to the QuickSpec ATE system, and a
  discussion of the results.
\end{itemize}

Section \ref{sec:background} describes the ATE problem in more detail, along
with existing approaches and their evaluation methodologies. We explain our
proposal for a more general benchmark in section \ref{sec:proposal} and
section \ref{sec:application} shows the results when applied to existing ATE
tools. Analysis of these results is given in section \ref{sec:discussion} and
concluding remarks in \ref{sec:conclusion}.

@@

The task of discovering theorems in an arbitrary theory can be
described as the interplay of several processes: (i) formulating new
definitions and concepts; (ii) finding patterns suitable for posing as
conjectures; and (iii) proving that those conjectures are theorems.
The latter is studied extensively in the field of Automated Theorem
Proving (ATP). Far less attention has been paid to automating the
first two tasks, which both Automated Theory Formation (ATF) and
Automated Theory Exploration (ATE) address.  We discuss the
relationship between ATF and ATE in historical context in
$\S$\ref{exploration-versus-formation}.

A major challenge for both ATF and ATE is choosing how to narrow down
the set of generated conjectures to those deemed ``interesting'',
since this is an imprecise term with many different
interpretations. For example, all existing approaches agree that
simple tautologies are ``uninteresting'', but differ when it comes to
more complex statements.  Colton {\em et al.}  give a survey of
systems for theory formation and exploration, and their notions of
``interestingness'' for concepts and conjectures, identifying six
notions in total~\cite{colton2000notion}. These notions, as applied to ATE, are:

@@

\begin{table}
  \centering
  \begin{tabular}{ |l|l|c|c|c|c|c|c| }
    \hline
    \multirow{2}{*}{\textbf{Program}}                     &
    \multirow{2}{*}{\textbf{Conjecture Types}}            &
    \multicolumn{6}{c}{\textbf{Interestingness Measures}} \\ \hhline{~~------}
    \tRow{            &                    & \iE & \iN & \iS & \iA & \iC & \iU}
    \tRow{AM          & \tIFF, \tIMP, \tNE &   X &   X &   X &   X &   X &   X}
    \tRow{GT          & \tIFF, \tIMP, \tNE &   X &   X &   X &   X &   X &   X}
    \tRow{Graffiti    & \tINE              &   X &   X &   X &     &   X &   X}
    \tRow{Bagai et al & \tNE               &     &   X &     &   X &   X &    }
    \tRow{HR          & \tIFF, \tIMP, \tNE &   X &   X &   X &   X &   X &   X}
    \tRow{QuickSpec   & \tEQ               &   X &   X &     &   X &   X &    }
    \tRow{Speculate   & \tCON \tEQ / \tINE &   X &   X &     &   X &   X &    }
    \tRow{IsaCoSy     & \tEQ               &   X &   X &     &   X &   X &   X}
    \tRow{IsaScheme   & \tEQ               &   X &   X &     &   X &   X &   X}
  \end{tabular}
  \caption{Classification of ATE systems from \cite{colton2000notion}, extended
    to those compared in \cite{claessen2013automating} (QuickSpec is the
    conjecture generation component of HipSpec). The interestingness measures
    are \iE{}mpirical plausibility, \iN{}ovelty, \iS{}urprisingness,
    \iA{}pplicability, \iC{}omprehensibility (low complexity) and \iU{}tility.}
  \label{table:colton}
\end{table}

@@

We summarise the criteria in Table 1 and state which were used in key
ATF/ATE systems. The entries for AM, GT, Graffiti, Bagai et al. and HR are based
on this survey (the latter is Colton's own system). We extend this analysis to
some more recent systems in the remaining rows (based on our understanding of
their function): QuickSpec, Speculate~\cite{braquehais2017speculate}, IsaCoSy
and IsaScheme.

@@

With such ambiguous and varied goals, approaches and assessment criteria it is
difficult to compare ATE systems in a quantitative way, and hence to form some
measure of ``progress'' for the field. Our proposed benchmarking methodology
attempts to remedy this by setting a clear target, hopefully in line with the
myriad goals of existing researchers, whilst being generally applicable to
systems of this type.

@@

Differences in background and motivation continue to be relevant
today. While the majority of work in automating mathematics has been
in symbolic manipulation and theorem proving, we are concerned here
with other aspects of mathematics, including the construction of conjectures,
(counter-)examples and theorems. These tasks, along with the formation of new
definitions and concepts, are varyingly known as
``Automated Theory Formation''~\cite{lenat:77,colton:book},
``Automated Mathematical Theory Exploration'',
``Mathematical Theory Exploration''~\cite{buchberger:06} (also sometimes
prefaced with ``Computer-Aided'' or ``Algorithm-Supported''),
``Automated Mathematical Discovery''~\cite{epstein:91,colton:interestingness,esarm2008},
``Concept Formation in Discovery Systems''~\cite{haase}, and
``Automated Theorem Discovery''~\cite{roy}. Such a plethora of terminology can
be unhelpful and can mask similarities between the different fields. In
particular, the twin strands of Automated Theory Formation and
Automated Mathematical Theory Exploration seem to be developing
somewhat independently without a clear differentiating
methodology. Below we discuss commonalities and differences between
the two schools of thought.

@@

There are three aspects to consider when we evaluate an ATE system:

@@

This comparison uses \emph{precision/recall analysis}: a particular set of
definitions is chosen, such as those in figure \ref{figure:list_theory}, and a
\emph{ground truth} is chosen as the 'ideal' set of conjectures which we would
like an ATE system to produce from these definitions.

Each system is run, and their output compared to the ground truth. To score
100\% on precision and recall, an ATE system must output all of the conjectures
which appear in the ground truth, and nothing else:

@@

Our main contribution is a benchmarking methodology, shown in figure
\ref{figure:flow_chart}, which generates both a large definition/ground-truth
corpus (an order of magnitude larger than previous work) and a scalable,
statistical approach to evaluating ATE systems using this corpus. We follow a
precision/recall approach similar to the work described above, with the main
difference being the source of definitions and ground truths: we take existing
problem sets designed for automated \emph{theorem proving}, and adapt their
content for use in the \emph{theory exploration} setting.

@@

\begin{itemize}
\item For each problem, there should be a clear distinction between the theorem
  to be proved and the definitions involved, such that the two can be easily and
  meaningfully separated. This rules out problem sets like those of
  SMT-COMP~\cite{barrett2005smt}, where many problems involve uninterpreted
  functions, whose behaviour is \emph{implicit} in the logical structure of the
  theorem statement but not separately \emph{defined}.
\item Definitions should be \emph{strongly typed}, such that they can be
  translated into the native language of each ATE system (in this work, that
  includes Haskell\iffalse FIXME and Isabelle\fi).
\item The problem set should be relevant to the desired domain. In our case, we
  desire higher-order functions and inductively defined types, which rules out
  first-order languages/logics (such as TPTP~\cite{sutcliffe2009tptp}).
\item Since it will act as our ground truth, the problem set should ideally
  contain every ``interesting'' conjecture involving its included
  definitions. Realistically, we should aim for each definition to appear in
  \emph{many} theorem statements; rather than each problem having unique
  definitions.
\item The problem set should be as large as possible, for robustness of the
  resulting statistics.
\end{itemize}

Once such a problem set has been chosen, we must separate the definitions
referenced by the theorems from the theorem statements themselves. The former
will be used as input to the ATE systems under evaluation, whilst the latter
form a ground truth corpus against which to compare the ATE output.

It is important to ensure that there are no duplicate definitions: theory
exploration does not depend on the names of functions, so neither should our
analysis. For example, consider a problem set which includes a commutativity
theorem for a \texttt{plus} function, and an associativity theorem for an
\texttt{add} function, where the definitions of \texttt{plus} and \texttt{add}
are $\alpha$-equivalent. We would expect an ATE system to conjecture
commutativity and associativity for \emph{both} functions, or for \emph{neither}
function, since they're equivalent. Yet a na\"ive precision/recall analysis
would treat commutativity of \texttt{add} and associativity of \texttt{plus} as
\emph{uninteresting}, since they don't appear in the ground truth.

@@

We could, in theory, send these de-duplicated definitions straight into an ATE
system, and use the updated theorem statements as the ground truth for analysis.
However, this would cause two problems:

\begin{itemize}
\item The result would be a single data point, which makes it difficult to
  infer performance \emph{in general}.
\item It is impractical to run any existing ATE system on ``large'' inputs,
  containing more than around 10 definitions.
\end{itemize}

To solve both of these problems we instead \emph{sample} a subset of
definitions. Given a sample size, we choose a subset of that many definitions,
and use that as our ATE input. We generate a corresponding ground truth by
selecting those theorems from the corpus which only contain references to
definitions that appear in our sample.

Unfortunately, uniform sampling of definitions gives rise to a lottery: for a
large corpus and a fixed sample size, it becomes highly unlikely that a sample
will contain the particular definitions required by a theorem. This would cause
most samples to have an empty ground truth, and hence $0$ precision and
undefined recall \emph{independent} of what the ATE system produces. This is
clearly undesirable as an evaluation method.

@@

Given a sample of definitions and a corresponding ground truth, the actual
execution of the ATE system proceeds as in prior work. We must translate the
chosen definitions into the particular input format of the tool under study,
then we time the execution, with a timeout after e.g. 1 hour.

@@

This approach produces a single runtime, precision and recall value for each
sample. We propose two methods for analysing this data: \emph{summarising}
the performance of an ATE system, or \emph{comparing} the performance of
\emph{two} ATE systems.

@@

To encourage competition in the field, it is important to compare the relative
performance of different ATE systems on the same task. Since the aggregate
statistics in the above summaries do not include details of specific runs, any
comparison based on them would have very low statistical power, and therefore it
is appropriate to use an alternative approach when comparing.

@@

    % Evaluation section
    \path let \p{pad}  = (pad),
              \p{sthm} = (sthm)
           in coordinate (runPos) at (\x{pad}, \y{sthm});
    \node (run) [process, below=of runPos]{Run ATE system};
    \node (pr)  [process, below=of run]{Analysis};

@@

% All together, TIP provides 219 distinct function definitions and 343
%   theorem statements, which is enough to fully exercise current ATE systems.
% Benchmark problems include examples from the theorem proving literature
%   as well as common program verification tasks, ensuring the resulting corpus is
%   relevant to researchers and practitioners.
% TIP's maintainers provide a set of tools, including translators from TIP's
%   native format (based on SMT-Lib~\cite{BarFT-SMTLIB}) to Haskell and Isabelle
%   (which are used by ATE systems).

% To aid reproducibility, we use a cryptographic hash as our source of randomness:
% the $n$th sample of size $s$ uses the SHA256 hash of $n$, $s$ and the definition
% corpus; the latter prevents tailoring the corpus to influence the choices,
% although ATE systems could .

@@

The key to our benchmarking methodology is the simplifying assumption that
theorem proving problem sets are a good proxy for desirable ATE output. This
allows us to side-step the philosophical quagmire of ``interestingness'' to
produce concrete, measurable values; it is also a core weakness, as there are
compelling reasons to refute it.

@@

Notably, if ATE matures to the point of providing \emph{truly novel} insights,
even in well-studied domains, then the assumptions we rely on break down because
such results cannot (by definition) appear in any existing corpus.

>>>>

\begin{abstract}
  We propose a benchmark suite for evaluating the efficiency and effectiveness
  of \emph{conjecture formation} by automated tools for \emph{mathematical
    theory exploration} in higher-order, inductive theories; a domain especially
  suited for analysing software. By providing standard tools and metrics, we
  hope to encourage innovation and comparison between the disparate approaches
  currently being pursued, and spur improvements similar to those seen in the
  competitive field of automated theorem proving.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\emph{Conjecture generation/formation}, a sub-field of \emph{mathematical theory
  exploration} (MTE), is the open-ended problem of producing conjectures about a
given logical theory which are somehow ``interesting''.

This has applications wherever we find use for formal statements: in proof
assistants and their libraries, in mathematics education and research, and in
the specification, verification, optimisation and testing of software.

@@

We attempt to solve this discrepancy, at least for the foreseeable future, by
defining a standard, unambiguous benchmarking approach with which to compare
the conjecture generation of MTE systems. Our contributions include:

\begin{itemize}
\item A general methodology for benchmarking conjecture generation.
\item Resolving the issue of ``interestingness'' through the use of
  theorem-proving benchmarks as a ground-truth.
\item A specific instantiation of this methodology, using the Tons of Inductive
  Problems benchmark as a corpus.
\item Automated tooling to perform this benchmarking.
\item Application of our methodology to the QuickSpec MTE system, and a
  discussion of the results.
\end{itemize}

Section \ref{sec:background} describes MTE and the conjecture generation problem
in more detail, along with existing approaches and their evaluation
methodologies. We explain our proposal for a more general benchmark in section
\ref{sec:proposal} and section \ref{sec:application} shows the results when
applied to existing MTE tools. Analysis of these results is given in section
\ref{sec:discussion} and concluding remarks in \ref{sec:conclusion}.

@@

The task of discovering theorems in an arbitrary theory can be
described as the interplay of several processes: (i) formulating new
definitions and concepts; (ii) finding patterns suitable for posing as
conjectures; and (iii) proving that those conjectures are theorems.
The latter is studied extensively in the field of Automated Theorem
Proving (ATP). Far less attention has been paid to automating the
first two tasks, which both Automated Theory Formation (ATF) and
Mathematical Theory Exploration (MTE) address.  We discuss the relationship
between ATF and ATE in historical context in
$\S$\ref{exploration-versus-formation}.

A major challenge for both ATF and MTE is choosing how to narrow down
the set of generated conjectures to those deemed ``interesting'', since this is
an imprecise term with many different interpretations. For example, all existing
approaches agree that simple tautologies are ``uninteresting'', but differ when
it comes to more complex statements.  Colton {\em et al.} give a survey of
systems for theory formation and exploration, and their notions of
``interestingness'' for concepts and conjectures, identifying six notions in
total~\cite{colton2000notion}. These notions, as applied to conjectures, are:

@@

\begin{table}
  \centering
  \begin{tabular}{ |l|l|c|c|c|c|c|c| }
    \hline
    \multirow{2}{*}{\textbf{Program}}                     &
    \multirow{2}{*}{\textbf{Conjecture Types}}            &
    \multicolumn{6}{c}{\textbf{Interestingness Measures}} \\ \hhline{~~------}
    \tRow{            &                    & \iE & \iN & \iS & \iA & \iC & \iU}
    \tRow{AM          & \tIFF, \tIMP, \tNE &   X &   X &   X &   X &   X &   X}
    \tRow{GT          & \tIFF, \tIMP, \tNE &   X &   X &   X &   X &   X &   X}
    \tRow{Graffiti    & \tINE              &   X &   X &   X &     &   X &   X}
    \tRow{Bagai et al & \tNE               &     &   X &     &   X &   X &    }
    \tRow{HR          & \tIFF, \tIMP, \tNE &   X &   X &   X &   X &   X &   X}
    \tRow{QuickSpec   & \tEQ               &   X &   X &     &   X &   X &    }
    \tRow{Speculate   & \tCON \tEQ / \tINE &   X &   X &     &   X &   X &    }
    \tRow{IsaCoSy     & \tEQ               &   X &   X &     &   X &   X &   X}
    \tRow{IsaScheme   & \tEQ               &   X &   X &     &   X &   X &   X}
  \end{tabular}
  \caption{Classification of MTE systems from \cite{colton2000notion}, extended
    to those compared in \cite{claessen2013automating} (QuickSpec is the
    conjecture generation component of HipSpec). The interestingness measures
    are \iE{}mpirical plausibility, \iN{}ovelty, \iS{}urprisingness,
    \iA{}pplicability, \iC{}omprehensibility (low complexity) and \iU{}tility.}
  \label{table:colton}
\end{table}

@@

We summarise the criteria in Table 1 and state which were used in key
ATF/MTE systems. The entries for AM, GT, Graffiti, Bagai et al. and HR are based
on this survey (the latter is Colton's own system). We extend this analysis to
some more recent systems in the remaining rows (based on our understanding of
their function): QuickSpec, Speculate~\cite{braquehais2017speculate}, IsaCoSy
and IsaScheme.

@@

With such ambiguous and varied goals, approaches and assessment criteria it is
difficult to compare MTE systems in a quantitative way, and hence to form some
measure of ``progress'' for the field. Our proposed benchmarking methodology
attempts to remedy this by setting a clear target, hopefully in line with the
myriad goals of existing researchers, whilst being generally applicable to
systems of this type.

@@

Differences in background and motivation continue to be relevant
today. While the majority of work in automating mathematics has been
in symbolic manipulation and theorem proving, we are concerned here
with other aspects of mathematics, including the construction of conjectures,
(counter-)examples and theorems. These tasks, along with the formation of new
definitions and concepts, are varyingly known as
``Automated Theory Formation''~\cite{lenat:77,colton:book},
``Mathematical Theory Exploration''~\cite{buchberger:06} (also sometimes
prefaced with ``Computer-Aided'', ``Automated'' or ``Algorithm-Supported''),
``Automated Mathematical Discovery''~\cite{epstein:91,colton:interestingness,esarm2008},
``Concept Formation in Discovery Systems''~\cite{haase}, and
``Automated Theorem Discovery''~\cite{roy}. Such a plethora of terminology can
be unhelpful and can mask similarities between the different fields. In
particular, the twin strands of Automated Theory Formation and
Automated Mathematical Theory Exploration seem to be developing
somewhat independently without a clear differentiating
methodology. Below we discuss commonalities and differences between
the two schools of thought.

@@

There are three aspects to consider when we evaluate an MTE system:

@@

This comparison uses \emph{precision/recall analysis}: a particular set of
definitions is chosen, such as those in figure \ref{figure:list_theory}, and a
\emph{ground truth} is chosen as the 'ideal' set of conjectures which we would
like an MTE system to produce from these definitions.

Each system is run, and their output compared to the ground truth. To score
100\% on precision and recall, an MTE system must output all of the conjectures
which appear in the ground truth, and nothing else:

@@

Our main contribution is a benchmarking methodology, shown in figure
\ref{figure:flow_chart}, which generates both a large definition/ground-truth
corpus (an order of magnitude larger than previous work) and a scalable,
statistical approach to evaluating MTE systems using this corpus. We follow a
precision/recall approach similar to the work described above, with the main
difference being the source of definitions and ground truths: we take existing
problem sets designed for automated \emph{theorem proving}, and adapt their
content for use in the \emph{theory exploration} setting.

@@

\begin{itemize}
\item For each problem, there should be a clear distinction between the theorem
  to be proved and the definitions involved, such that the two can be easily and
  meaningfully separated. This rules out problem sets like those of
  SMT-COMP~\cite{barrett2005smt}, where many problems involve uninterpreted
  functions, whose behaviour is \emph{implicit} in the logical structure of the
  theorem statement but not separately \emph{defined}.
\item Definitions should be \emph{strongly typed}, such that they can be
  translated into the native language of each MTE system (in this work, that
  includes Haskell\iffalse FIXME and Isabelle\fi).
\item The problem set should be relevant to the desired domain. In our case, we
  desire higher-order functions and inductively defined types, which rules out
  first-order languages/logics (such as TPTP~\cite{sutcliffe2009tptp}).
\item Since it will act as our ground truth, the problem set should ideally
  contain every ``interesting'' conjecture involving its included
  definitions. Realistically, we should aim for each definition to appear in
  \emph{many} theorem statements; rather than each problem having unique
  definitions.
\item The problem set should be as large as possible, for robustness of the
  resulting statistics.
\end{itemize}

Once such a problem set has been chosen, we must separate the definitions
referenced by the theorems from the theorem statements themselves. The former
will be used as input to the MTE systems under evaluation, whilst the latter
form a ground truth corpus against which to compare the MTE output.

It is important to ensure that there are no duplicate definitions: theory
exploration does not depend on the names of functions, so neither should our
analysis. For example, consider a problem set which includes a commutativity
theorem for a \texttt{plus} function, and an associativity theorem for an
\texttt{add} function, where the definitions of \texttt{plus} and \texttt{add}
are $\alpha$-equivalent. We would expect an MTE system to conjecture
commutativity and associativity for \emph{both} functions, or for \emph{neither}
function, since they're equivalent. Yet a na\"ive precision/recall analysis
would treat commutativity of \texttt{add} and associativity of \texttt{plus} as
\emph{uninteresting}, since they don't appear in the ground truth.

@@

We could, in theory, send these de-duplicated definitions straight into an MTE
system, and use the updated theorem statements as the ground truth for analysis.
However, this would cause two problems:

\begin{itemize}
\item The result would be a single data point, which makes it difficult to
  infer performance \emph{in general}.
\item It is impractical to run any existing MTE system on ``large'' inputs,
  containing more than around 10 definitions.
\end{itemize}

To solve both of these problems we instead \emph{sample} a subset of
definitions. Given a sample size, we choose a subset of that many definitions,
and use that as our MTE input. We generate a corresponding ground truth by
selecting those theorems from the corpus which only contain references to
definitions that appear in our sample.

Unfortunately, uniform sampling of definitions gives rise to a lottery: for a
large corpus and a fixed sample size, it becomes highly unlikely that a sample
will contain the particular definitions required by a theorem. This would cause
most samples to have an empty ground truth, and hence $0$ precision and
undefined recall \emph{independent} of what the MTE system produces. This is
clearly undesirable as an evaluation method.

@@

Given a sample of definitions and a corresponding ground truth, the actual
execution of the MTE system proceeds as in prior work. We must translate the
chosen definitions into the particular input format of the tool under study,
then we time the execution, with a timeout after e.g. 1 hour.

@@

This approach produces a single runtime, precision and recall value for each
sample. We propose two methods for analysing this data: \emph{summarising}
the performance of an MTE system, or \emph{comparing} the performance of
\emph{two} MTE systems.

@@

To encourage competition in the field, it is important to compare the relative
performance of different MTE systems on the same task. Since the aggregate
statistics in the above summaries do not include details of specific runs, any
comparison based on them would have very low statistical power, and therefore it
is appropriate to use an alternative approach when comparing.

@@

    % Evaluation section
    \path let \p{pad}  = (pad),
              \p{sthm} = (sthm)
           in coordinate (runPos) at (\x{pad}, \y{sthm});
    \node (run) [process, below=of runPos]{Run MTE system};
    \node (pr)  [process, below=of run]{Analysis};

@@

% All together, TIP provides 219 distinct function definitions and 343
%   theorem statements, which is enough to fully exercise current MTE systems.
% Benchmark problems include examples from the theorem proving literature
%   as well as common program verification tasks, ensuring the resulting corpus is
%   relevant to researchers and practitioners.
% TIP's maintainers provide a set of tools, including translators from TIP's
%   native format (based on SMT-Lib~\cite{BarFT-SMTLIB}) to Haskell and Isabelle
%   (which are used by MTE systems).

% To aid reproducibility, we use a cryptographic hash as our source of randomness:
% the $n$th sample of size $s$ uses the SHA256 hash of $n$, $s$ and the definition
% corpus; the latter prevents tailoring the corpus to influence the choices,
% although MTE systems could .

@@

The key to our benchmarking methodology is the simplifying assumption that
theorem proving problem sets are a good proxy for desirable MTE output. This
allows us to side-step the philosophical quagmire of ``interestingness'' to
produce concrete, measurable values; it is also a core weakness, as there are
compelling reasons to refute it.

@@

Notably, if MTE matures to the point of providing \emph{truly novel} insights,
even in well-studied domains, then the assumptions we rely on break down because
such results cannot (by definition) appear in any existing corpus.
